\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{accent}{HTML}{000000}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{nosep, leftmargin=1.5em, topsep=2pt}


\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]

\titlespacing*{\section}{0pt}{6pt}{4pt}

\begin{document}


{\LARGE\bfseries Kripesh Pandit} \hfill
\small
\href{mailto:kripesh.pandit21@gmail.com}{kripesh.pandit21@gmail.com} $|$ \href{https://linkedin.com/in/kripesh-pandit}{linkedin.com/in/kripesh-pandit}
\section{Education}
\textbf{Fisk University Nashville, TN} \hfill  \\
\textit{Bachelor of Science in Computer Science} \hfill \textit{ -- }
\vspace{2pt}







\section{Technical Skills}
\begin{itemize}[label={}]
  \item \textbf{Languages:} Python, C++, C, HTML/CSS, JavaScript, Kotlin, SQL
  \item \textbf{Technologies/Frameworks:} MongoDB, Android Studio, GitHub, VS Code, Figma, Adobe Analytics, React, A/B
  \item \textbf{Skills:} testing, Jira
  \item \textbf{PM Skills:} Wireframing, PRD, Stakeholder Management, Creative Thinking, Product Roadmapping, Branding \&
\end{itemize}






\section{Nepal Student Association Fisk University}
\begin{itemize}
  \item Vice President Aug 2022 – Pressent
  \item Spearheaded cultural programs that attracted 200+ attendees, strengthening community engagement and
  \item showcasing organizational impact.
  \item Secured funding and managed budgets to deliver high-quality events, ensuring alignment of resources with
  \item organizational goals.
  \item Delegated tasks across a 10-member executive team, fostering accountability and efficient execution of
  \item strategic initiatives.
  \item Collaborated with university administration and external partners to promote cross-cultural understanding
  \item and increase visibility of the association.
  \item MSIPP: Department of Energy June 2024 – August 2024
\end{itemize}


\section{Machine Learning Intern}
\textbf{Designed and tested machine learning models for an intrusion detection system on smart grids to} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{identify and minimize cyber attacks, using TensorFlow, scikit-learn, TensorFlow Federated, and} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}







\section{Python.}
\begin{itemize}
  \item Compared centralized models and federated counterparts on F1 score, accuracy, and precision.
  \item Simulated smart meter devices with Raspberry Pi and federated learning to analyze power consumption and
  \item network latency.
  \item Hydrogel Design January 2023 – July 2023
\end{itemize}


\section{Research Assistant}
\textbf{Implemented a MongoDB database for research articles, using HTML, CSS, and Python for secure testing} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{and backtracking.} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Studied molecular simulations, clarifying molecular interactions and structural behavior.} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Conducted market analysis on hydrogel network formation in polyglycolic-based networks to inform} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{product strategy.} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{EVOK Creative Studio Nashville, TN} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Product Manager Intern May 2024 – July 2024} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Drove product ideation via market research and user feedback; produced wireframes and user flows; led} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{full-stack Android app development with React Native.} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Implemented the foundation for dark mode and additional themes, improving UI flexibility and user} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{engagement in testing (90\% approval on functionality).} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Home Depot Nashville, TN} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Tech Innovation and App Strategy Extern September 2023 – November 2023} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Led an interactive mobile app feature targeting Gen Z, raising engagement by 15\% and improving conversion} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{(KPI) by 10\% via A/B testing and data analysis.} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Presented insights and app evolution strategies to senior stakeholders, informing the roadmap for Gen Z} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{market engagement.} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}





\section{Projects}
\textbf{Music Generation System May 2024}





\section{Personal Project}
\textbf{}
\begin{itemize}
  \item Built a system that generates jazz melodies using RNNs and LSTMs.
  \item Used Music21 for preprocessing/post-processing and TensorFlow for training and evaluation.
  \item Represented melodies as time-series and trained a generative-style classification ML model.
\end{itemize}
\textbf{Full-Stack MERN Web App}
\begin{itemize}
  \item Developed a social media web app with MongoDB, Express.js, React.js, Node.js and RESTful APIs;
\end{itemize}
\textbf{implemented JWT auth; features include posts, likes, and follow/unfollow.}
\begin{itemize}
  \item Built responsive UI with React and Material-UI; used Redux for state management and dynamic routing.
  \item Implemented backend services with Node/Express and MongoDB; added profile editing, follower tracking, and
\end{itemize}
\textbf{Technical Program Manager Scholar January 2023}
 $|$ \textit{May 2023}\begin{itemize}
  \item Applied agile principles to guide “Team Turing” through sprints, delivering “FiskBook” from concept to
\end{itemize}
\textbf{presentation in 24 hours.}
\begin{itemize}
  \item Led ideation, design, development, and delivery; received “Honorable Mention” for execution and innovation.
\end{itemize}




\section{Leadership}
\textbf{Goldman Sachs Possibilities Summit (2024), US Army xTECH (2024), Meta Scholar Cohort 3 (2023), HBCU} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}\textbf{Near-Peer Mentor (2023), RippleMatch Leadership Development Extern (2023)} \hfill  \\
\textit{} \hfill \textit{ -- }
\vspace{2pt}



\end{document}